Assessing linkages between watershed nutrient loading and water quality in a subtropical estuary with semiparametric models.

### 2023-04-20 Schramm_2023_02_PLOS/Schramm_2023_02_PLOS.qmd
Plos draft rejected :sad:

## this sets our default code chunk options
knitr::opts_chunk$set(echo = FALSE,
                      ## figure chunk options
                      dev = "CairoTIFF",
                      dpi = 300,
                      fig.align = "center",
                      out.width = "100%")

@@

p1 / p2 / p3 / guide_area() + plot_layout(guides = 'collect',
                                          design = layout)

>>>>

## this sets our default code chunk options
knitr::opts_chunk$set(echo = FALSE,
                      ## figure chunk options
                      dev = "CairoPS",
                      dpi = 600,
                      fig.align = "center",
                      out.width = "100%")

@@

p4 <- p1 / p2 / p3 / guide_area() + plot_layout(guides = 'collect',
                                          design = layout)

p4
